When two-point correlation function fails to describe a structure...

### 2024-03-12 paper.tex
Prove blue text

\textcolor{blue}{It is trivial to prove that $\sum_if_i^2 = \sum_i\tilde{f}_i^2$
  where $f_i$ and $\tilde{f}_i$ are coefficients of $f$ and $\tilde{f}$
  respectively. Indeed, $f$ and $\tilde{f}$ have the same correlation function,
  and evaluating $S_2(0)$ gives us the desired result. We also make a conjecture
  that $f$ and $\tilde{f}$ have the same number of non-zero coefficients and
  thus, all coefficients of $\tilde{f}$ are either $0$ or $1$.}
\textcolor{red}{It's better to find a proof for this claim, but no bad things
  can happen, if we cannot.}

>>>>

\textcolor{red}{The idea of proof for this lemma is a contribution of Kolya and
  Oleg}.
Now the following lemma shows that $\tilde{f}$ is a polynomial with coefficients
being equal to 0 or 1:
\begin{lemma}
  Let $f \in \mathbb{Z}[x]$ is a polynomial with coefficients in $\{0, 1\}$
  which factors as $f(x) = \prod_{i=1}^n f_i(x)$. A polynomial
  $\tilde{f}(x) = \prod_k f_k(x) \prod_l x^{\deg f_l} f_l(x^{-1})$ where $k$
  runs through some subset $K$ of $N = \{1, \dots, n\}$ and $l$ runs through
  $N \setminus K$ has also its coefficients in $\{0, 1\}$.
\end{lemma}
\begin{proof}
  In this proof we assume $f(0) = 1$ for simplicity.

  Suppose $n = 1$. Then $\tilde{f}$ is either the reciprocal of $f$ or $f$ itself.

  Suppose $n = 2$ and write $f = gh$. In two trivial cases when $K = \emptyset$
  or $K = N$ we have $\tilde{f}$ to be equal either the reciprocal of $f$ or
  $f$. Let $\tilde{f}(x) = \tilde{g}(x)h(x)$,
  $\tilde{g}(x) = x^{\deg g}g(x^{-1})$. As shown above, $f$ and $\tilde{f}$ have
  the same two-point correlation functions, i.e.
  $s_f(t) = s_{\tilde{f}}(t)$. Comparing free coefficients of $s_f(t)$ and
  $s_{\tilde{f}}(t)$ we obtain the following relation for coefficients of $f$:
  \begin{equation}
    \sum_{k=0}^d f_k^2 = \sum_{k=0}^d \tilde{f}_k^2
    \label{eq:squares-equal}
  \end{equation}
  where $d = \deg f = \deg \tilde{f}$. Now we have this chain of equalities
  \begin{equation}
    \begin{aligned}
    \sum_{k=0}^d f_k = f(1) &= g(1) h(1) = \sum_{k=0}^{d_g} g_k \sum_{k=0}^{d_h} h_k \\
    = \sum_{k=0}^{d_g} g_{d_g-k} \sum_{k=0}^{d_h} h_k &= \tilde{g}(1) h(1) =
    \tilde{f}(1) = \sum_{k=0}^d \tilde{f}_k
    \end{aligned}
    \label{eq:coeff-equal}
  \end{equation}

  For any $m \in \mathbb{Z} \setminus \{0, 1\}$ we have $m^2 > m$. Taking into
  account \cref{eq:coeff-equal} and letting any coefficient of $\tilde{f}$ be
  in set $\mathbb{Z} \setminus \{0, 1\}$ we get a contradiction with
  \cref{eq:squares-equal}. This contradiction proves this case.

  Now suppose $n > 2$. We can construct products
  $\tilde{g}(x) = \prod_l x^{\deg f_l }f_l(x^{-1})$ and $h(x) = \prod_k f_k(x)$
  and continue with the proof for $n = 2$.
\end{proof}
